### 2023-11-14 Scripts/Manuscript/manuscript.Rmd
added the exploratory analyses results tables.

# creating an empty dataframe to store the results in
cfa_results <- data.frame(RMSEA = 0,
                          N_factors = 0,
                          Single_factor = FALSE)

@@

@@

  # adding a single factor check indicator value
  single_factor <- ifelse(RMSEA_value < 0.08 | parallel_N_factors == 1, TRUE, 
                          FALSE)

@@

INSERT FIGURE 46 HERE

```{r Plot 46 Initial Data Code, include = FALSE, eval = FALSE}
# Initial
ggplot(plot_46_data, aes(QMP_ratio, QMP_Rep_ratio)) + 
  geom_point() +
  geom_jitter(width = 0.05, height = 0.05) +
  stat_smooth(method="lm") + 
  theme_bw() +
  theme(strip.text.y = element_text(size = 7), strip.background = element_rect(
    color = "black", fill = "white", size = 1, linetype = "solid"
  )) +
  xlab("QMP Ratio (Original)") + ylab("QMP Ratio (Replication)") +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) + 
  facet_grid(vars(QMP_Rep_type), vars(QMP_type))

@@

1
```{r Plot 46 Revised Data Code}
# Revised
ggplot(plot_46_data_rev, aes(QMP_ratio, QMP_Rep_ratio)) + 
  geom_point() +
  geom_jitter(width = 0.05, height = 0.05) +
  stat_smooth(method="lm") + 
  theme_bw() +
  theme(strip.text.y = element_text(size = 7), strip.background = element_rect(
    color = "black", fill = "white", size = 1, linetype = "solid"
  )) +
  xlab("QMP Ratio (Original)") + ylab("QMP Ratio (Replication)") +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) + 
  facet_grid(vars(QMP_Rep_type), vars(QMP_type))

@@

```{r}
#apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)

# $\left(B = -0.963, t(70.319) = -1.491, p = .011 \right)$

@@

INSERT QMP REPLICATION ASSOCIATION TESTS TABLE

INSERT QMP ORIGINAL REPLICATION ASSOCIATION TESTS TABLE

@@

INSERT FACTOR ANALYSES RESULTS TABLE HERE

>>>>

# creating an empty dataframe to store the results in
cfa_results <- data.frame(RMSEA = 0,
                          N_factors = 0,
                          Single_factor = "")

@@

  if(is.null(RMSEA_value) != TRUE){
    RMSEA_value <- apa_num(RMSEA_value, digits = 3)
  }

@@

  # adding a single factor check indicator value
  single_factor <- ifelse(RMSEA_value < 0.08 | parallel_N_factors == 1, "Yes", 
                          "No")

@@

```{r Plot 46 Initial Data Code, include = FALSE, eval = FALSE, error = FALSE}
# Initial
ggplot(plot_46_data, aes(QMP_ratio, QMP_Rep_ratio)) + 
  geom_point() +
  geom_jitter(width = 0.05, height = 0.05) +
  stat_smooth(method="lm") + 
  theme_bw() +
  theme(strip.text.y = element_text(size = 7), strip.background = element_rect(
    color = "black", fill = "white", size = 1, linetype = "solid"
  )) +
  xlab("QMP Ratio (Original)") + ylab("QMP Ratio (Replication)") +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) + 
  facet_grid(vars(QMP_Rep_type), vars(QMP_type))

@@

```{r Plot 46 Revised Data Code, error = FALSE}
# Revised
ggplot(plot_46_data_rev, aes(QMP_ratio, QMP_Rep_ratio)) + 
  geom_point() +
  geom_jitter(width = 0.05, height = 0.05) +
  stat_smooth(method="lm") + 
  theme_bw() +
  theme(strip.text.y = element_text(size = 7), strip.background = element_rect(
    color = "black", fill = "white", size = 1, linetype = "solid"
  )) +
  xlab("QMP Ratio (Original)") + ylab("QMP Ratio (Replication)") +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) + 
  facet_grid(vars(QMP_Rep_type), vars(QMP_type))

@@

```{r H6 Exploratory Associations Revised Table}
# creating the dataframe for the table
H6_table_dataframe_l_REV <- rbind(Results_H6_between_REV$def_def, Results_H6_between_REV$def_op,
  Results_H6_between_REV$def_sel, Results_H6_between_REV$def_quant, Results_H6_between_REV$def_mod, 
  Results_H6_between_REV$op_def, Results_H6_between_REV$op_op, Results_H6_between_REV$op_sel, 
  Results_H6_between_REV$op_quant, Results_H6_between_REV$op_mod, Results_H6_between_REV$sel_def, 
  Results_H6_between_REV$sel_op, Results_H6_between_REV$sel_sel, Results_H6_between_REV$sel_quant, 
  Results_H6_between_REV$sel_mod)

H6_table_dataframe_r_REV <- rbind(Results_H6_between_REV$quant_def, Results_H6_between_REV$quant_op,
  Results_H6_between_REV$quant_sel, Results_H6_between_REV$quant_quant, Results_H6_between_REV$quant_mod, 
  Results_H6_between_REV$mod_def, Results_H6_between_REV$mod_op, Results_H6_between_REV$mod_sel, 
  Results_H6_between_REV$mod_quant, Results_H6_between_REV$mod_mod, Results_H6_between_REV$tot_def, 
  Results_H6_between_REV$tot_op, Results_H6_between_REV$tot_sel, Results_H6_between_REV$tot_quant, 
  Results_H6_between_REV$tot_mod)

H6_table_dataframe_REV <- cbind(H6_table_dataframe_l_REV, H6_table_dataframe_r_REV)

# adding asterices for significance to the significant p in the dataframe
H6_table_dataframe_REV[11,3] <- paste0(H6_table_dataframe_REV[11,3], "$^*$")
H6_table_dataframe_REV[13,3] <- paste0(H6_table_dataframe_REV[13,3], "$^*$")
H6_table_dataframe_REV[14,3] <- paste0(H6_table_dataframe_REV[14,3], "$^*$")
H6_table_dataframe_REV[4,6] <- paste0(H6_table_dataframe_REV[4,6], "$^*$")
H6_table_dataframe_REV[11,6] <- paste0(H6_table_dataframe_REV[11,6], "$^*$")
H6_table_dataframe_REV[13,6] <- paste0(H6_table_dataframe_REV[13,6], "$^*$")
H6_table_dataframe_REV[14,6] <- paste0(H6_table_dataframe_REV[14,6], "$^*$")

# adding a column to help indicate the original QMP type
H6_table_dataframe_REV_expanded <- cbind(c("Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification"), H6_table_dataframe_REV)

# adding rows to give indication of specific sections (apa_table being awkward)
H6_table_REV_for_printing <- rbind(c("QMP Type", "", "Definition", "", "", "Quantification", ""), H6_table_dataframe_REV_expanded[1:5,], c("QMP Type", "", "Operationalisation", "", "", "Modification", ""),  H6_table_dataframe_REV_expanded[(6:10),], c("QMP Type", "", "Selection", "", "", "Total", ""), H6_table_dataframe_REV_expanded[(11:15),])

colnames(H6_table_REV_for_printing) <-  c("Original", "$b$", "SD", "$p$", "$b$", "SD", "$p$")

# print the table in apa formatting
apa_table(
  H6_table_REV_for_printing, align = c("l", "r", "c", "r", "r", "c", "r")
  , caption = "Beta Regression Test Results for the Association between Replication
QMP Ratio and Original QMP Ratio as obtained using the Revised Protocol"
  , note = "Rows indicate Original QMP type, and within table indicates Replication QMP type. Sample size for comparisons involving modification were lower since not all measures were modified. Therefore the standard errors are larger. $^* p < .05$"
  , escape = FALSE, placement= "ht", midrules = c(1, 6, 7, 12, 13))

### Possible change: omit sd and p-value, and instead show CI and n, in which case also the note should be changed.

@@

```{r H6 Exploratory Associations Initial Table}
# creating the dataframe for the table
H6_table_dataframe_l <- rbind(Results_H6_between$def_def, Results_H6_between$def_op,
  Results_H6_between$def_sel, Results_H6_between$def_quant, Results_H6_between$def_mod, 
  Results_H6_between$op_def, Results_H6_between$op_op, Results_H6_between$op_sel, 
  Results_H6_between$op_quant, Results_H6_between$op_mod, Results_H6_between$sel_def, 
  Results_H6_between$sel_op, Results_H6_between$sel_sel, Results_H6_between$sel_quant, 
  Results_H6_between$sel_mod)

H6_table_dataframe_r <- rbind(Results_H6_between$quant_def, Results_H6_between$quant_op,
  Results_H6_between$quant_sel, Results_H6_between$quant_quant, Results_H6_between$quant_mod, 
  Results_H6_between$mod_def, Results_H6_between$mod_op, Results_H6_between$mod_sel, 
  Results_H6_between$mod_quant, Results_H6_between$mod_mod, Results_H6_between$tot_def, 
  Results_H6_between$tot_op, Results_H6_between$tot_sel, Results_H6_between$tot_quant, 
  Results_H6_between$tot_mod)

H6_table_dataframe <- cbind(H6_table_dataframe_l, H6_table_dataframe_r)

# adding asterices for significance to the significant p in the dataframe
H6_table_dataframe[8,3] <- paste0(H6_table_dataframe[8,3], "$^*$")
H6_table_dataframe[11,3] <- paste0(H6_table_dataframe[11,3], "$^*$")
H6_table_dataframe[14,3] <- paste0(H6_table_dataframe[14,3], "$^*$")
H6_table_dataframe[8,6] <- paste0(H6_table_dataframe[8,6], "$^*$")
H6_table_dataframe[9,6] <- paste0(H6_table_dataframe[9,6], "$^*$")
H6_table_dataframe[11,6] <- paste0(H6_table_dataframe[11,6], "$^*$")
H6_table_dataframe[13,6] <- paste0(H6_table_dataframe[13,6], "$^*$")

# adding a column to help indicate the original QMP type
H6_table_dataframe_expanded <- cbind(c("Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification"), H6_table_dataframe)

# adding rows to give indication of specific sections (apa_table being awkward)
H6_table_for_printing <- rbind(c("QMP Type", "", "Definition", "", "", "Quantification", ""), H6_table_dataframe_expanded[1:5,], c("QMP Type", "", "Operationalisation", "", "", "Modification", ""),  H6_table_dataframe_expanded[(6:10),], c("QMP Type", "", "Selection", "", "", "Total", ""), H6_table_dataframe_expanded[(11:15),])

colnames(H6_table_for_printing) <-  c("Original", "$b$", "SD", "$p$", "$b$", "SD", "$p$")

# print the table in apa formatting
apa_table(
  H6_table_for_printing, align = c("l", "r", "c", "r", "r", "c", "r")
  , caption = "Beta Regression Test Results for the Association between Replication
QMP Ratio and Original QMP Ratio as obtained using the Initial Protocol"
  , note = "Rows indicate Original QMP type, and within table indicates Replication QMP type. Sample size for comparisons involving modification were lower since not all measures were modified. Therefore the standard errors are larger. $^* p < .05$"
  , escape = FALSE, placement= "ht", midrules = c(1, 6, 7, 12, 13))

@@

```{r Unidimesnionality Test Results Table}
# add the names of the relevant papers and a shortcut for the measure used.
cfa_results_expanded <- cbind(c("Caruso et al. (2012)", "Husnu & Crisp (2010)", "Nosek et al. (2002), Art", "Nosek et al. (2002), Math", "Van Lange et al. (1997)", "Anderson et al. (2012), SWL", "Anderson et al. (2012), PA", "Anderson et al. (2012), NA", "Giessner & Schubert (2007)", "Norenzayan et al. (2002)", "Zhong & Liljenquist (2006)", "Monin & Miller (2001), most", "Monin & Miller (2001), some", "Cacioppo et al. (1983), elm", "Cacioppo et al. (1983), nfc", "De Fruyt et al. (2000), consc", "Albarracín et al. (2008), exp. 5", "Shnabel & Nadler (2008)", "Vohs & Schooler (2008)"), cfa_results)

# adding sensible column names
colnames(cfa_results_expanded) <- c("Original Article", "RMSEA", "N Factors", "Unidimensional")

# Renaming the columns for the not converged cfa.
cfa_results_for_print <- cfa_results_expanded
cfa_results_for_print$RMSEA[16] <- "Did"
cfa_results_for_print$`N Factors`[16] <- "Not"
cfa_results_for_print$Unidimensional[16] <- "Converge"

# print the table in apa formatting
apa_table(
  cfa_results_for_print, align = c("l", "r", "r", "r")
  , caption = "RMSEA and Parallel Analysis Suggested Factors based on Factor Analysis
for Measure Data", note = "N Factors refer to the number of factors suggested based on parallel analysis of the measure data. The word or abbreviation after the author names and year indicates the specific measure within that original article that was analysed.", escape = FALSE, row.names = FALSE, placement= "ht")
